%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Chi Hui}{Ng}{ \urlstyle{same}\href{https://www.linkedin.com/in/chihui/}{linkedin.com/in/chihui/}| \href{https://github.com/Chihui8199}{github.com/Chihui8199}\\
\href{https://chihui.netlify.app/}{chihui.netlify.app} | 91689895 | \href{mailto:NGCH0118@e.ntu.edu.sg}{NGCH0118@e.ntu.edu.sg}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Nanyang Technological \\ University}
\descript{Double Degree Programme Bachelor of Business (with Specialisation in Business Analytics)
and Bachelor of Engineering (Computer Science)}
\location{May 2023 | Singapore, SG}
Distinction\\
\sectionsep

\subsection{NANYANG JUNIOR COLLEGE}
\location{GCE A Levels, 5 Distinctions}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links} 
%Facebook:// \href{https://facebook/dd}{\bf dd} \\
%Github:// \href{https://github.com/deedydas}{\bf deedydas} \\
%LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\bf debarghyadas} \\
%YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\bf DeedyDash007} \\
%Twitter://  \href{https://twitter.com/debarghya_das}{\bf @debarghya\_das} \\
%Quora://  \href{https://www.quora.com/Debarghya-Das}{\bf Debarghya-Das}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{}Java 
\textbullet{}Python 
\textbullet{}R
\textbullet{}JavaScript
\textbullet{}HTML
\textbullet{}CSS
\textbullet{}ReactJS
\textbullet{}Django
\textbullet{}Git
\textbullet{}Microsoft Office Suite
\textbullet{}PowerBI
\textbullet{}Tableau
\textbullet{}MySQL
\textbullet{}NoSQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CO-CURRICULAR ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CO-CURRICULAR ACTIVITIES}

\runsubsection{Student Entrepreneurship Programme}
\descript{| Co-Founder }
\location{May 2021 - Aug 2021}
Secured \$3000 in funding to work on a sustainable technology startup in food industry 

\sectionsep
\runsubsection{Welfare Service Club}
\descript{| Director of Events}
\location{Aug 2019 - Aug 2021}
Organized large scale charity and bonding events for >1000 members.Secured \$2000 funding from Housing Development Board for implementation of events at 20 Senior Activity Centers.
\sectionsep

\sectionsep
\runsubsection{University YMCA}
\descript{| Director of Community Service Programme }
\location{Aug 2019 - Aug 2021}
Led team of 15 in mentoring of 20 ITE students, prepared marketing materials such as posters, forms, and messages.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Internships
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internships}
\runsubsection{Toku}
\descript{| Software Engineer Intern }
\location{Aug 2021 - Sept 2021 | Singapore, SG}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Design and build backend software of client contact manager for Toku admins to manage their customer information; Utilizing Django to develop the website whilst hosting the database on MySQL server.
\end{tightemize}
\sectionsep

\runsubsection{Accredify}
\descript{| Data Analyst Intern }
\location{May 2021 – Aug 2021 | Singapore, SG}
\begin{tightemize}
\item Designed product metrics and built data pipelines to create interactive dashboards (PowerBI \& Tableau), allowing tracking of internal analytics; reduced time spent on manual data extraction and analysis by 15\%. Value added by providing analysis and recommendation into usage analytics.
\item Developed API connector to allow data extraction and flow to dashboards for usage and financial reporting.
\item Wrote browser and unit tests (i.e., Login, Password Reset) for automated testing of software; reduced manual testing time
by 5\%. Applied industry Git, Jira and UAT practices during development and deployment phases.
\end{tightemize}
\sectionsep

\runsubsection{XinCap Group}
\descript{| Venture Analyst Intern }
\location{May 2020 – Aug 2020 | Singapore, SG}
\begin{tightemize}
\item Headed and established business partnerships with strategic partners resulting in a 112\% increase in MoM sales, 51\% increase in basket value.
\item Performed Search Engine Marketing by running Ads and A/B testing to track performance and optimise for spend.
\item Optimised existing dashboards (i.e., inventory, production, sales) and introduced forecasting models (Excel) for demand planning - to predict stock production and allocation.
\item Improved cemani.sg Shopify website by implementing email subscription pop-up, generating up to 10% more leads.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Projects}
\runsubsection{Software Systems Analysis \& Design Project}
\descript{| Educational Huf }
\location{Aug 2021 – Nov 2021 | Singapore, SG}
\begin{tightemize}
\item Developed a web-based educational game that allows users to create quizzes with multiple gaming levels.
\item Responsible for the front-end development of this project; Designed in-game answers and Ui interaction components utilising React.js. 
\end{tightemize}
\sectionsep

\runsubsection{Advanced Software Engineering Project}
\descript{| GoldFolks }
\location{Aug 2021 – Nov 2021 | Singapore, SG}
\begin{tightemize}
\item Developed an all-in-one elderly management application system using Flutter; key features of the app includes ability to set medication reminders, ability to play cognitive games and ability to watch different exercise videos.
\item Contributed to the whole software development lifecycle by conducting requirement analysis, planning, designing, developing and testing of the assets.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
